---
title: "data_import"
output: github_document
---

will be focusing of readr package in tidyverse library today.

```{r setup}
library(tidyverse)
```

## Read in some data

Read in the litters dataset.

```{r}
litters_df = read.csv("./data_import_examples/FAS_litters.csv")

litters_df = janitor::clean_names(litters_df)
```

read.csv from readr package

**janitor::clean_names** use clean_names function in janitor package. No need to library(janitor). Use when this is the only function used from janitor in this code.


## Take a look at the data 

printing in the console

```{r}
litters_df
```

```{r}
head(litters_df)
```

```{r}
tail(litter)
```

```{r}
skimr::skim(litters_df)
```

also you can put "V iew(litters_df)" in console to view dataframe. 

## Options to read csv

```{r}
litters_df = read_csv("./data_import_examples/FAS_litters.csv", skip = 10, col_names = FALSE)
```

_col_names = FALSE_ indicated there is no seperate column name row, this way the first row is kept as column names.  
