---
title: "data_import"
output: github_document
---

will be focusing of readr package in tidyverse library today.

```{r setup}
library(tidyverse)
library(readxl)
library(haven)
```

## Read in some data

Read in the litters data set.

```{r}
litters_df = read_csv("./data_import_examples/FAS_litters.csv")

litters_df = janitor::clean_names(litters_df)
```

read_csv from readr package

**janitor::clean_names** use clean_names function in janitor package. No need to library(janitor). Use when this is the only function used from janitor in this code.


## Take a look at the data 

printing in the console

```{r}
litters_df
```

```{r}
head(litters_df)
```

```{r}
tail(litters_df)
```

```{r}
skimr::skim(litters_df)
```

also you can put "V iew(litters_df)" in console to view dataframe. 

## Options to read csv

Skipping first several rows
```{r}
litters_df = read_csv("./data_import_examples/FAS_litters.csv", skip = 10, col_names = FALSE)
```

_col_names = FALSE_ indicated there is no column names row, this way the Xn are used as default column names instead of reading the first row as column names.  

```{r}
litters_df = read_csv("./data_import_examples/FAS_litters.csv", na = c("", "NA",999, "."))
```

_na = c()_ detect content in the list and take them as NA when reading csv

### Column types

Check out ?read_csv()

## Other file formats

### Read in an excel file. 

```{r}
mlb_df = read_excel("./data_import_examples/mlb11.xlsx", range = "A1:F7")
mlb_df
```

#### read excel options

check ?read_excel

_sheet_ when there is multiple sheets in excel file
_range_ to specify row or column range to read in 

### Read SAS file

```{r}
pulse_df = read_sas("./data_import_examples/public_pulse_data.sas7bdat")
pulse_df 
```

## comparison with base R

what about read.csv in base R?

```{r}
litters_base = read.csv("./data_import_examples/FAS_litters.csv")
litters_readr = read_csv("./data_import_examples/FAS_litters.csv")

litters_base
litters_readr
```

read r version is more organized and less recognition mistakes

## Export dataset

Export mlb sub-table

```{r}
write_csv(mlb_df, "./data_import_examples/mlb_subtable.csv") 
```


